---
title: "Lee Gianetti's Homework 2"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
---

```{r setup, include=FALSE}
library(flexdashboard) # always
```

## Sidebar {.sidebar}

Prepare a dashboard using the **mtcars** data. You need to write the code to actually replicate the same plots you are seeing.

1.  Send the link to the code in a GitHub repository
2.  Dashboard should be published from a GitHub repo
3.  The README should include the dashboard link.

**NOTE**: You may vary titles and colors.

Row
--------------------------------

### THREE-GEARCARS ARE DOMINANT

```{r}
## for plot1.rds
link1="https://github.com/dataviz690/hw-test/raw/main/del1Draft.rds"
readRDS(url(link1))
```

### FEW CARS have SIX or more CARBURATORS

```{r}
## for plot2.rds
link2="https://github.com/dataviz690/hw-test/raw/main/del2Draft.rds"
readRDS(url(link2))
```

Row
----------------------------------------

### Only 5-gear cars utilize the 6 and 8 carburetor setups.

```{r}
## for plot3.rds
link3="https://github.com/dataviz690/hw-test/raw/main/del3Draft.rds"
readRDS(url(link3))
```


